\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
fixed issued with multi-clumn figure in paper
minor edits to sec I through IV

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available. The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multiagent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Routing and Transportation Analyzer}, designed for optimizing
autonomous traffic at a city-wide scale. AORTA creates scale simulations of the
real world by generating maps using publicly available road data from
\textit{OpenStreetMap} (OSM). This allows simulations to be set up through AORTA
for a desired region anywhere in the world in a matter of minutes. AORTA allows
for traffic optimization by creating intelligent behaviors for individual driver
agents and intersection policies to be followed by these agents. These behaviors
and policies define how agents interact with one another, control when they
cross intersections, and route agents to their destination. This paper
demonstrates a simple application using AORTA through an experiment testing an
intersection policy designed for autonomous vehicles at a city-wide scale.

@@

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the
competing teams completed the 96km course set for the DARPA Urban Challenge
\cite{spectrumUrbanChallenge2007}. They did so while obeying the traffic laws
followed by human drivers, navigating along with other moving vehicles, and
following correct intersection precedence order. Since then, Google's driverless
cars have clocked more than 250,000km on public roads in urban California, USA
\cite{tedThrun2011}. In 2010, researchers from the University of Parma
successfully completed an autonomous \textit{intercontinental} run from Parma,
Italy to Shanghai, China \cite{cnnVislab2010}. The successful completion of all
these milestones suggests that autonomous cars are here to stay, and are ever
closer to becoming commercially available. With the arrival of autonomous cars,
it also becomes possible to optimize traffic in ways not possible for human
drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be trimmed}

@@

\begin{figure}[t]
  \centering \includegraphics[width=\linewidth]{downtown_atx.png}
  \caption{A simulation of downtown Austin, Texas.}
  \label{fig:ui_screenshot}
  \vspace{-15pt}
\end{figure}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}, a platform designed for testing autonomous vehicle
behaviors and intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and decide
on both long term and short term actions. AORTA allows for the creation of
intersection policies that designate when agents can cross the intersection.
AORTA's goal is to allow for the definition of new agent behaviors and
intersection policies to optimize autonomous traffic. Additionally, by
assigning human-like behaviors such as the ``car following model''
\cite{brackstone1999car} to agents, and traffic-signal-like policies to
intersections, AORTA could potentially simulate human traffic.

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation of
the real world in a few minutes. AORTA is available open-source and is easily
extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}} \commentpk{could also change this
to a citation}, making it easier for users to test out a number of agent
behaviors and intersection policies.

This paper explores the state-of-the-art in traffic simulators in section
\ref{sec:related_work}, followed by a description of AORTA's architecture in
section \ref{sec:arch}.  Use of OSM data in AORTA is explained in section
\ref{sec:map}, along with a description of the simulator and the default
behaviors available in AORTA in section \ref{sec:simulation}. An experiment
investigating the benefit of an alternate intersection policy designed for
autonomous vehicles is presented in \ref{sec:results}. The paper then concludes
with a discussion on future work.

@@

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans to
minimize traffic delays while minimizing the total amount of time by which agents
are late to their destinations. This goal is somewhat different from that of AORTA,
where the routes (demand) supplied by individuals is taken as is and does not have
a pre-determined ideal time of arrival. Rather than improving agent routes, AORTA
allows creating entirely different behaviors for both vehicles and intersections
in order to simulate a different environment instead of optimizing plans for a
society in a static environment.

@@

Simulators have also focused on autonomous vehicles with sensors and actuators
\cite{figueiredo2009approach}. These simulators are used to ensure that
autonomous vehicles are behaving correctly while interacting with other
vehicles and infrastructure, given their configuration of sensors and
actuators. On the other hand, AORTA assumes that autonomous vehicles have
reasonable sensory input and mechanical output, and instead focuses on
interactions between an agent and its surrounding agents and intersections.

@@

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-20pt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \subfloat[An agent cannot turn left while agents on the perpendicular road
  cross]{
    \includegraphics[scale=0.4]{turn_conflicts.png}
    \label{fig:conflicts}
  }
  ~ % horizontal spacing, mostly for the sake of the captions
  \subfloat[A difficult intersection to tile in New Orleans, Louisiana. Note
  there are no overpasses pictured.]{
    \includegraphics[scale=0.4]{crazy_intersection.png}
    \label{fig:crazyIntersection}
  }
  \caption{Examples of AORTA's modeling of intersections and turns}
  \vspace{-15pt}
\end{figure}

@@

@@

\begin{figure*}[h]
  \centering
  \subfloat[Average delay in Austin]{
    \includegraphics[width=0.5\linewidth]{avg_lag_agent_atx.png}
    \label{fig:avg_lag_atx}
  }
  \subfloat[Average delay in Houston]{
    \includegraphics[width=0.5\linewidth]{avg_lag_agent_houston.png}
    \label{fig:avg_lag_houston}
  }
\end{figure*}
\begin{figure*}[h]
  \subfloat[Number of agents driving in Austin]{
    \includegraphics[width=0.5\linewidth]{agent_cnt_atx.png}
    \label{fig:agent_cnt_atx}
  }
  \subfloat[Number of agents driving in Houston]{
    \includegraphics[width=0.5\linewidth]{agent_cnt_houston.png}
    \label{fig:agent_cnt_houston}
  }
  \caption{Autonomous reservations outperform stop signs and traffic signals in
           these experiments.}
  %\vspace{-10pt}
\end{figure*}

@@

\section*{ACKNOWLEDGMENTS}

>>>>

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available. The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multiagent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Routing and Transportation Analyzer}, designed for optimizing
autonomous traffic at a city-wide scale. AORTA creates scale simulations of the
real world by generating maps using publicly available road data from
\textit{OpenStreetMap} (OSM). This allows simulations to be set up through
AORTA for a desired region anywhere in the world in a matter of minutes. AORTA
allows for traffic optimization by creating intelligent behaviors for
individual driver agents and intersection policies to be followed by these
agents. These behaviors and policies define how agents interact with one
another, control when they cross intersections, and route agents to their
destination. This paper demonstrates a simple application using AORTA through
an experiment testing intersection policies at a city-wide scale.

@@

% In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
% Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2007, six of the competing teams completed the 96km course set for the DARPA
Urban Challenge In 2004, the farthest distance traveled by a vehicle
autonomously in the DARPA \cite{spectrumUrbanChallenge2007}. They did so while
obeying the traffic laws followed by human drivers, navigating along with other
moving vehicles, and following correct intersection precedence order. Since
then, Google's driverless cars have clocked more than 250,000km on public roads
in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the
University of Parma successfully completed an autonomous
\textit{intercontinental} run from Parma, Italy to Shanghai, China
\cite{cnnVislab2010}. The successful completion of all these milestones
suggests that autonomous cars are here to stay, and are ever closer to becoming
commercially available. With the arrival of autonomous cars, it also becomes
possible to optimize traffic in ways not possible for human drivers. 
%\commentd{If we need space, I agree with Dr Chiu, some of this could be
%trimmed}

@@

\begin{figure}[t]
  \centering \includegraphics[width=\linewidth]{downtown_atx.png}
  \caption{A simulation of autonomous agents in downtown Austin, Texas, as visualized through the UI available within the AORTA simulator}
  \label{fig:ui_screenshot}
  \vspace{-15pt}
\end{figure}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}, a platform designed for testing autonomous vehicle
behaviors and intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. Intersection policies
deisgnate when it is safe for an agent to cross an intersection.  AORTA's goal
is to allow for the definition of new agent behaviors and intersection policies
to optimize autonomous traffic. Additionally, by assigning human-like behaviors
such as the ``car following model'' \cite{brackstone1999car} to agents, and
traffic-signal-like policies to intersections, AORTA could potentially simulate
human traffic.

% AORTA allows for the creation of
% intersection policies that designate when agents can cross the intersection.

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation
of the real world in a few minutes. AORTA is available open-source and is
easily extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easier for users to
test out a number of agent behaviors and intersection policies in a short
timespan.

This paper explores the state-of-the-art in traffic simulators in section
\ref{sec:related_work}, followed by a description of AORTA's architecture in
section \ref{sec:arch}.  Use of OSM data in AORTA is explained in section
\ref{sec:map}, along with a description of the simulator in section
\ref{sec:simulation}. A simple experiment is presented in section
\ref{sec:results} demonstrating an application built on top of AORTA, that
evaluates different intersection policies in a large scale scenario. The paper
then concludes with a discussion on future work.

@@

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans to
minimize traffic delays while minimizing the total amount of time by which
agents are late to their destinations. This goal is somewhat different from
that of AORTA, where the routes (demand) supplied by individuals is taken as is
and does not have a pre-determined ideal time of arrival. Rather than improving
agent routes, AORTA allows creating entirely different behaviors for both
vehicles and intersections in order to simulate a different environment instead
of optimizing plans for a society in a static environment \commentpk{I think
MIke made these changes last night, but I am not sure if the last few sentences
are clear to me}.

@@

% Simulators have also focused on autonomous vehicles with sensors and actuators
% \cite{figueiredo2009approach}. These simulators are used to ensure that
% autonomous vehicles are behaving correctly while interacting with other
% vehicles and infrastructure, given their configuration of sensors and
% actuators. On the other hand, AORTA assumes that autonomous vehicles have
% reasonable sensory input and mechanical output, and instead focuses on
% interactions between an agent and its surrounding agents and intersections.

@@

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-15pt}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \subfloat[An agent cannot turn left while agents on the perpendicular road
  cross]{
    \includegraphics[width=0.42\columnwidth]{turn_conflicts.png}
    \label{fig:conflicts}
  }
  ~ % horizontal spacing, mostly for the sake of the captions
  \subfloat[A difficult intersection to tile in New Orleans, Louisiana. Note
  there are no overpasses pictured.]{
    \includegraphics[width=0.4\columnwidth]{crazy_intersection.png}
    \label{fig:crazyIntersection}
  }
  \caption{Examples of AORTA's modeling of intersections and turns}
  \vspace{-15pt}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \subfloat[Average delay in Austin]{
    \label{fig:avg_lag_atx}
    \includegraphics[width=0.4\textwidth]{avg_lag_agent_atx.png}
  }\,
  \subfloat[Average delay in Houston]{
    \label{fig:avg_lag_houston}
    \includegraphics[width=0.4\textwidth]{avg_lag_agent_houston.png}
  }\\
  \subfloat[Number of agents driving in Austin]{
    \label{fig:agent_cnt_atx}
    \includegraphics[width=0.4\textwidth]{agent_cnt_atx.png}
  }\,
  \subfloat[Number of agents driving in Houston]{
    \label{fig:agent_cnt_houston}
    \includegraphics[width=0.4\textwidth]{agent_cnt_houston.png}
  }
  \caption{Autonomous reservations outperform stop signs and traffic signals in
           these experiments.}
  \label{fig:results}
  \vspace{-15pt}
\end{figure*}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\small
\section*{ACKNOWLEDGMENTS}
